Methods for Polyphonic Music Transcription

### 2013-12-11 paper/paper.tex
added stuff to intro, data

% This is just copied from 'A Connectionist Approach to Automatic Transcription of Polyphonic Piano Music' for now:
Applications of a music transcription are versatile. Transcription produces a compact and standardized parametric representation of music. Such representation is needed for content-based retrieval of music in most current musical databases. It is useful in music analysis systems for tasks such as melody extraction, music segmentation and rhythm tracking. Transcription aids musicologists in analyzing music that has never been written down, such as improvised or ethnical music. The conversion of an acoustical waveform into parametric description is also useful in the process of making music, as well as in newer coding standards, such as MPEG-4, which may include such descriptions.

@@

\subsubsection{HMM smoothing}
In many of the techniques used (such as SVM's), notes at a single time step are classified independently of the notes at adjacent time steps. Since these methods do not take advantage of the temporal structure of piano music, hidden Markov models are often used for post-processing the output of the discriminative models. We model each note independently using a two-state HMM, where the states correspond to the note being on or off. The transition matrix and state priors can be estimated from the ground truth piano roll, while the emission matrix can be estimated using the output from the classifier as the observable variables. Applying the Viterbi algorithm to each note class results in a smoother piano roll that eliminates unlikely, spurious, isolated notes.

@@

\subsubsection{Reported measures}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & Score \\ \hline
SVM & 21\% & 21 \\ \hline
SVM with HMM & 22\% & 22 \\ \hline
NMF & 23\% & 23 \\ \hline
Sparse NMF & 24\% & 24 \\ \hline
AdaBoost & 25\% & 25 \\ \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & Score \\ \hline
SVM & 18\% & 18 \\ \hline
SVM with HMM & 19\% & 19 \\ \hline
NMF & 20\% & 20 \\ \hline
Sparse NMF & 21\% & 21 \\ \hline
AdaBoost & 22\% & 22 \\ \hline
\end{tabular}
\end{center}

@@

Beethoven & Sonata No. 5, Op. 10 (Prestissimo), Sonata No. 8, Op. 13 (Rondo Allegro) & Sonata No. 11, Op. 22 (Minuetto), Sonata No. 21, Op. 53 (Adagio molto) \\

>>>>

% This is just copied from 'A Connectionist Approach to Automatic Transcription of Polyphonic Piano Music' for now:
Music transcription is the process of creating a musical score from an audio recording.  There are many applications of music transcription. Transcription produces a compact and standardized parametric representation of music, which is necessary for content-based retrieval of music in most current musical databases. It is also useful in music analysis systems for tasks such as melody extraction, music segmentation and rhythm tracking. Transcription aids musicologists in analyzing music that has never been written down, such as improvised or ethnical music. The conversion of an acoustical waveform into parametric description is also useful in the process of making music, as well as in newer coding standards, such as MPEG-4, which may include such descriptions.

Historically, the task of music transcription has been left to expert musicians.  However, the process is difficult and time-consuming for complex recordings.  Thus the ability to automatically transcribe music is of both practical and theoretical interest.

@@

\subsubsection{HMM smoothing}
\begin{figure*}[t]
\begin{center}
\subfigure[]{
\includegraphics[scale=.6]{raw_svm}
}
\subfigure[]{
\includegraphics[scale=.6]{smoothed_svm}
}
\end{center}
\caption{ Many of the classifiers do not take temporal structure into account.  HMM smoothing captures some of this structure.  (a)  The estimated piano-roll before HMM smoothing. (b)  The estimated piano-roll after HMM smoothing}
\end{figure*}
In many of the techniques used (such as SVM's), notes at a single time step are classified independently of the notes at adjacent time steps. Since these methods do not take advantage of the temporal structure of piano music, hidden Markov models are often used for post-processing the output of the discriminative models. We model each note independently using a two-state HMM, where the states correspond to the note being on or off. The transition matrix and state priors can be estimated from the ground truth piano roll, while the emission matrix can be estimated using the output from the classifier as the observable variables. Applying the Viterbi algorithm to each note class results in a smoother piano roll that eliminates unlikely, spurious, isolated notes.

@@

\subsubsection{Reported measures}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 67.7\% & NR \\ \hline
SVM with HMM & 70\% & 34.2 \\ \hline
NMF & 23\% & 23 \\ \hline
Sparse NMF & 24\% & 24 \\ \hline
AdaBoost & 25\% & 25 \\ \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 51.7\% & 84.7  \\ \hline
SVM with HMM & 62.7\% & 53.8  \\ \hline
NMF & 20\% & 20 \\ \hline
Sparse NMF & 21\% & 21 \\ \hline
AdaBoost & 22\% & 22 \\ \hline
\end{tabular}
\end{center}

@@

Beethoven & Sonata No. 5, Op. 10 (Prestissimo), Sonata No. 8, Op. 13 (Rondo Allegro), For Elise (Poco moto) & Sonata No. 11, Op. 22 (Minuetto), Sonata No. 21, Op. 53 (Adagio molto) \\
